---
title: "Emotional Go/No-Go R Markdown"
author: "Michael J Colwell"
date: "17/02/2022"
output: html_document
---

```{r setup, include=FALSE}

```

## Emotional Go/No-Go RMarkdown (February 17, 2022; Version 0.1)

This is an RMarkdown to allow for reproducible and accurate preprocessing of the Emotional Go/No-Go Psychopy 
task data created by Michael Colwell (michael.colwell@psych.ox.ac.uk / ORCID 0000-0001-7846-2879).

The task materials and preprocessing script are offered free of charge for researchers. **It is requested that researchers who publish data using these materials (task or preprocessing script) cite the code for the task
in relevant publications**. Our reference is:

[TO BE COMPLETED]

##Required R packages

You will need the following packages installed and loaded before executing the below code chunks. 

```{r libraries, echo=FALSE, include=FALSE}

library(dplyr)
library(tidyverse)
library(gtools)
library(knitr)

```


##Begin preprocessing: Setting directory, merging files and deleting unnecessary columns

You will first need to point to the directory of your task files, typically in the 'data' subfolder where the
psychopy task is located. **Please edit the path directory below after the setwd function.**

The next lines in the chunk of code will allow you to merge all data files (.csv) in the directory assigned above to a dataframe, and then delete extraneous columns from the dataframe.

**Potential error**: "Error in rbind(deparse.level, ...) : numbers of columns of arguments do not match"
**Solution**: One of the .csv files may not have run beyond the practice section, therefore not enough columns
have generated. Delete this file and then continue.


```{r b0, echo=FALSE, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)

setwd("C:/Users/micha/Desktop/TestGo")

GoNo_files <- list.files(pattern=glob2rx("*No*.csv"))
GoNo <- do.call(rbind, lapply(GoNo_files, function(x) read.csv(x, stringsAsFactors = FALSE)))

GoNo <- GoNo %>% rename(Task.version=Task.Version..required.to.run., Participant.ID=participant)

GoNo <- GoNo %>% select(Participant.ID, Study.Name,Task.version, PRE.POST,frameRate,Express,Instructions,FaceE,ColourT, Pract.corr, Pract.rt,ISIjitterPractice,PracticeFace.started,key_resp.corr,key_resp.rt,ISIjitter,FaceSet.started,Instructions,CondFile)

GoNo <- GoNo %>%
  mutate(key_resp.rt = key_resp.rt*1000, Pract.rt = Pract.rt*1000,  ISI.time = ISIjitter*100, ISI.time.pract = ISIjitterPractice*100)

GoNo <- GoNo %>% mutate(ISI = coalesce(ISI.time, ISI.time.pract))

GoNo <- GoNo %>% mutate(FaceSet.started = as.numeric(FaceSet.started))

GoNo <- GoNo %>% mutate(FaceSetStart = coalesce(PracticeFace.started, FaceSet.started))

GoNo <- GoNo %>% mutate(Correct = coalesce(Pract.corr, key_resp.corr))

GoNo <- GoNo %>% mutate(Response.Time = coalesce(key_resp.rt, Pract.rt))

GoNo <- GoNo %>% select (-c(ISIjitter,ISIjitterPractice))


```

#Running data quality tests

```{r b0, echo=FALSE, include=TRUE}


samplesize = length(unique(GoNo$Participant.ID))

#Participant.ID may have two visits

print(samplesize)

ifelse((trialcount=80), print("PASS"), print("FAIL"))

trialcount<-plyr::count(GoNo$CondFile)

CheckFpsRange<- range(GoNo$frameRate)

Checkfps<-as.data.frame(table(GoNo$frameRate))
Checkfps <- Checkfps %>% mutate(FPSChecker = case_when((Freq==524) ~ 'No frames dropped', 
                             TRUE ~ "Frame drops detected - check original data file"))

paste("Your fps range is ", CheckFpsRange[1], "-", CheckFpsRange[2], ". Any significant deviation from the testing computer monitor native refresh rate needs to be queried as may indicate software lag.", sep="")

print(Checkfps)
rm(Checkfps)
rm(CheckFpsRange)


```

##Further parsing the dataframe 

The following chunks will allow you to parse the data, including generating omission/comission error checks
based on conditions set in the file.


```{r b0, echo=FALSE, include=TRUE}
GoNo <- GoNo %>%
  mutate(InhibitionType = case_when(str_detect(Instructions, "blue") ~ 'BlueInhibition', 
                             str_detect(Instructions, "yellow") ~ 'YellowInhibition',
                             TRUE ~ "NA"))
GoNo <- GoNo %>%
  mutate(OmComCheck = case_when((InhibitionType == "BlueInhibition" & ColourT == "Blue") ~ 'CommissionCheck',
                                (InhibitionType == 'BlueInhibition' & ColourT == 'Yellow') ~ 'OmissionCheck',
                                (InhibitionType == 'YellowInhibition' & ColourT == 'Yellow') ~ 'CommissionCheck',
           (InhibitionType == 'YellowInhibition' & ColourT == 'Blue') ~ 'OmissionCheck', 
         TRUE ~ "NA"))

GoNo <- GoNo %>%
  mutate(OmComFreq = case_when((OmComCheck == "CommissionCheck" & Correct == 1) ~ 'ComPass',
                                (OmComCheck == 'OmissionCheck' & Correct == 1) ~ 'OmPass',
                                (OmComCheck == 'CommissionCheck' & Correct == 0) ~ 'ComError',
           (OmComCheck == 'OmissionCheck' & Correct == 0) ~ 'OmError', 
         TRUE ~ "NA"))


GoNo <- GoNo %>%
  mutate(CorrectOm = case_when(str_detect(OmComFreq, "OmPass") ~ 1, 
                             TRUE ~ 0))
GoNo <- GoNo %>%
  mutate(CorrectCom = case_when(str_detect(OmComFreq, "ComPass") ~ 1, 
                             TRUE ~ 0))
GoNo <- GoNo %>%
  mutate(FailOm = case_when(str_detect(OmComFreq, "OmError") ~ 1, 
                             TRUE ~ 0))
GoNo <- GoNo %>%
  mutate(FailCom = case_when(str_detect(OmComFreq, "ComError") ~ 1, 
                             TRUE ~ 0))

GoNo <- GoNo %>%
  mutate(RealorPractice = case_when((Pract.corr==0) ~ 'Practice', (Pract.corr==1) ~ 'Practice',
                                    (key_resp.corr==0) ~ 'RealTask',(key_resp.corr==1) ~ 'RealTask', TRUE ~ 'NA'))
GoNo <- GoNo %>%
  mutate(HotorColdTrial = case_when(str_detect(Express, "Fear") ~ 'Hot', 
                             str_detect(Express, "Happy") ~ 'Hot',
                             str_detect(Express, "Scramble")~ 'Cold',
                             TRUE ~ "NA"))

GoNo <- GoNo %>% mutate(ValOmComFreq = case_when((OmComCheck == "CommissionCheck" & Express=="Fear" & key_resp.corr == 1) ~ 'FearComPass', (OmComCheck == "OmissionCheck" & Express=="Fear" & key_resp.corr == 1) ~ 'FearOmPass',(OmComCheck == "OmissionCheck" & Express=="Fear" & key_resp.corr == 0) ~ 'FearOmFail',(OmComCheck == "CommissionCheck" & Express=="Fear" & key_resp.corr == 0) ~ 'FearComFail', (OmComCheck == "CommissionCheck" & Express=="Happy" & key_resp.corr == 1) ~ 'HappyComPass', (OmComCheck == "OmissionCheck" & Express=="Happy" & key_resp.corr == 1) ~ 'HappyOmPass',(OmComCheck == "OmissionCheck" & Express=="Happy" & key_resp.corr == 0) ~ 'HappyOmFail',(OmComCheck == "CommissionCheck" & Express=="Happy" & key_resp.corr == 0) ~ 'HappyComFail', TRUE ~ "NA"))

GoNo <- GoNo %>% mutate(ColdHotOmComFreq = case_when((OmComCheck == "CommissionCheck" & HotorColdTrial=="Hot" & key_resp.corr == 1) ~ 'HotComPass', (OmComCheck == "OmissionCheck" & HotorColdTrial=="Hot" & key_resp.corr == 1) ~ 'HotOmPass',(OmComCheck == "OmissionCheck" & HotorColdTrial=="Hot" & key_resp.corr == 0) ~ 'HotOmFail',(OmComCheck == "CommissionCheck" & HotorColdTrial=="Hot" & key_resp.corr == 0) ~ 'HotComFail', (OmComCheck == "CommissionCheck" & HotorColdTrial=="Cold" & key_resp.corr == 1) ~ 'ColdComPass', (OmComCheck == "OmissionCheck" & HotorColdTrial=="Cold" & key_resp.corr == 1) ~ 'ColdOmPass',(OmComCheck == "OmissionCheck" & HotorColdTrial=="Cold" & key_resp.corr == 0) ~ 'ColdOmFail',(OmComCheck == "CommissionCheck" & HotorColdTrial=="Cold" & key_resp.corr == 0) ~ 'ColdComFail', TRUE ~ "NA"))

GoNo <- GoNo %>% mutate(PractColdHotOmComFreq = case_when((OmComCheck == "CommissionCheck" & HotorColdTrial=="Hot" & Pract.corr == 1) ~ 'HotComPass', (OmComCheck == "OmissionCheck" & HotorColdTrial=="Hot" & Pract.corr == 1) ~ 'HotOmPass',(OmComCheck == "OmissionCheck" & HotorColdTrial=="Hot" & Pract.corr == 0) ~ 'HotOmFail',(OmComCheck == "CommissionCheck" & HotorColdTrial=="Hot" & Pract.corr == 0) ~ 'HotComFail', (OmComCheck == "CommissionCheck" & HotorColdTrial=="Cold" & Pract.corr == 1) ~ 'ColdComPass', (OmComCheck == "OmissionCheck" & HotorColdTrial=="Cold" & Pract.corr == 1) ~ 'ColdOmPass',(OmComCheck == "OmissionCheck" & HotorColdTrial=="Cold" & Pract.corr == 0) ~ 'ColdOmFail',(OmComCheck == "CommissionCheck" & HotorColdTrial=="Cold" & Pract.corr == 0) ~ 'ColdComFail', TRUE ~ "NA"))

```

##Summaries for long file format

```{r b0, echo=FALSE, include=TRUE}

Long_GoNo_MainSummary <- GoNo %>%
  group_by(Participant.ID, PRE.POST, RealorPractice,  HotorColdTrial,Express)%>%
  summarise(RTmean = mean(Response.Time, na.rm=TRUE), RTsd = sd(Response.Time, na.rm=TRUE), AccurateOm = sum(CorrectOm), AccurateCom = sum(CorrectCom), MissOm= sum(FailOm), MissCom = sum(FailCom))

Long_GoNo_MainSummary <- Long_GoNo_MainSummary %>% filter(RealorPractice!="NA")

Long_GoNo_Summary_acrossOmCom <- GoNo %>%
  group_by(Participant.ID, RealorPractice,  OmComCheck,Express)%>%
  summarise(RTmean = mean(Response.Time, na.rm=TRUE), RTsd = sd(Response.Time, na.rm=TRUE), ISImean = mean(ISI, na.rm=TRUE), ISIsd = sd(ISI, na.rm=TRUE), face_appear_mean = mean(FaceSetStart,na.rm=TRUE), face_appear_sd = sd(FaceSetStart, na.rm=TRUE), AccurateOm = sum(CorrectOm), AccurateCom = sum(CorrectCom), MissOm= sum(FailOm), MissCom = sum(FailCom))

Long_GoNo_Summary_acrossOmCom <- Long_GoNo_Summary_acrossOmCom %>% filter(RealorPractice!="NA")

```

##Summaries for wide file format

```{r b0, echo=FALSE, include=TRUE}

WideGoNo <- GoNo

Wide_GoNo_MainSummary <- WideGoNo %>% filter(RealorPractice!="Practice")

Wide_GoNo_MainSummary <- WideGoNo %>% filter(HotorColdTrial!="NA")

Wide_GoNo_MainSummary <- WideGoNo %>%
  group_by(Participant.ID,  HotorColdTrial)%>%
  summarise(RTmean = mean(Response.Time, na.rm=TRUE), RTsd = sd(Response.Time, na.rm=TRUE), AccurateOm = sum(CorrectOm), AccurateCom = sum(CorrectCom), MissOm= sum(FailOm), MissCom = sum(FailCom))

Wide_GoNo_MainSummary <- Wide_GoNo_MainSummary %>% filter(RTsd!="NA")

##############Generate OmissionsTrue
Wide_GoNo_OmissionsTRUE <- Wide_GoNo_MainSummary %>% select(AccurateOm,HotorColdTrial)

Wide_GoNo_OmissionsTRUE <- Wide_GoNo_OmissionsTRUE %>% 
  spread(HotorColdTrial, AccurateOm,fill=FALSE)

Wide_GoNo_OmissionsTRUE <- Wide_GoNo_OmissionsTRUE %>%
  mutate(ColdOmTrue=Cold,HotOmTrue=Hot)
##############Generate ComissionsTRUE
Wide_GoNo_OmissionsTRUE <- Wide_GoNo_MainSummary %>% select(AccurateCom,HotorColdTrial)

Wide_GoNo_ComissionsTRUE <- Wide_GoNo_OmissionsTRUE %>% 
  spread(HotorColdTrial, AccurateCom,fill=FALSE)

Wide_GoNo_ComissionsTRUE <- Wide_GoNo_ComissionsTRUE %>%
  mutate(ColdComTrue=Cold,HotComTrue=Hot)
#################Generate OmissionsFalse
Wide_GoNo_OmissionsFALSE <- Wide_GoNo_MainSummary %>% select(MissOm,HotorColdTrial)

Wide_GoNo_OmissionsFALSE <- Wide_GoNo_OmissionsFALSE %>% 
  spread(HotorColdTrial, MissOm,fill=FALSE)

Wide_GoNo_OmissionsFALSE <- Wide_GoNo_OmissionsFALSE %>%
  mutate(ColdOmFalse=Cold,HotOmFalse=Hot)

##################Generate ComissionsFALSE (i.e. Omission error occurred)
Wide_GoNo_ComissionsFALSE <- Wide_GoNo_MainSummary %>% select(MissCom,HotorColdTrial)

Wide_GoNo_ComissionsFALSE <- Wide_GoNo_ComissionsFALSE %>% 
  spread(HotorColdTrial, MissCom,fill=FALSE)

Wide_GoNo_ComissionsFALSE <- Wide_GoNo_ComissionsFALSE %>%
  mutate(ColdComFalse=Cold,HotComFalse=Hot)

##################Generate RTmean (i.e. Commission error occurred)
Wide_GoNo_RTmean <- Wide_GoNo_MainSummary %>% select(RTmean,HotorColdTrial)

Wide_GoNo_RTmean <- Wide_GoNo_RTmean %>% 
  spread(HotorColdTrial, RTmean,fill=FALSE)

Wide_GoNo_RTmean <- Wide_GoNo_RTmean %>%
  mutate(HotRT=Hot,ColdRT=Cold)

#################Generate RTsd across hot/cold conditions

Wide_GoNo_RTsd <- Wide_GoNo_MainSummary %>% select(RTsd,HotorColdTrial)

Wide_GoNo_RTsd <- Wide_GoNo_RTsd %>% 
  spread(HotorColdTrial, RTsd,fill=FALSE)

Wide_GoNo_RTsd <- Wide_GoNo_RTsd %>%
  mutate(ColdRTsd=Cold,HotRTsd=Hot)
#################

Wide_GoNo_MainPre <- Wide_GoNo_RTmean %>% select(Participant.ID)

#Add columns together and remove extraneous df

Wide_GoNo_MainPre <- cbind(Wide_GoNo_MainPre, ColdOmTrue = Wide_GoNo_OmissionsTRUE$ColdOmTrue)
Wide_GoNo_MainPre <- cbind(Wide_GoNo_MainPre, HotOmTrue = Wide_GoNo_OmissionsTRUE$HotOmTrue)
Wide_GoNo_MainPre <- cbind(Wide_GoNo_MainPre, HotOmFalse = Wide_GoNo_OmissionsFALSE$HotOmFalse)
Wide_GoNo_MainPre <- cbind(Wide_GoNo_MainPre, ColdOmFalse = Wide_GoNo_OmissionsFALSE$ColdOmFalse)

Wide_GoNo_MainPre <- cbind(Wide_GoNo_MainPre, ColdComTrue = Wide_GoNo_ComissionsTRUE$ColdComTrue)
Wide_GoNo_MainPre <- cbind(Wide_GoNo_MainPre, HotComTrue = Wide_GoNo_ComissionsTRUE$HotComTrue)
Wide_GoNo_MainPre <- cbind(Wide_GoNo_MainPre, ColdComFalse = Wide_GoNo_ComissionsFALSE$ColdComFalse)
Wide_GoNo_MainPre <- cbind(Wide_GoNo_MainPre, HotComFalse = Wide_GoNo_ComissionsFALSE$HotComFalse)

Wide_GoNo_MainPre <- cbind(Wide_GoNo_MainPre, HotRTmean = Wide_GoNo_RTmean$HotRT)
Wide_GoNo_MainPre <- cbind(Wide_GoNo_MainPre, ColdRTmean = Wide_GoNo_RTmean$ColdRT)

Wide_GoNo_MainPre <- cbind(Wide_GoNo_MainPre, HotRTsd = Wide_GoNo_RTsd$HotRTsd)
Wide_GoNo_MainPre <- cbind(Wide_GoNo_MainPre, ColdRTsd = Wide_GoNo_RTsd$ColdRTsd)

Wide_GoNo_MainHotColdSeperate <-Wide_GoNo_MainPre

rm(Wide_GoNo_OmissionsTRUE)
rm(Wide_GoNo_OmissionsFALSE)
rm(Wide_GoNo_ComissionsTRUE)
rm(Wide_GoNo_ComissionsFALSE)
rm(Wide_GoNo_RTmean)
rm(Wide_GoNo_RTsd)
rm(WideGoNo)
rm(Wide_GoNo_MainPre)

#Spread by PRE/POST for RT (example)
Wide_GoNo_MainPREPOSTexample <- Wide_GoNo_MainPre %>%
  mutate(PRE.POST1 = case_when(grepl("2",Participant.ID, ignore.case = TRUE) ~ 'POST',
         TRUE ~ "PRE"))

Wide_GoNo_MainPREPOSTexample <- Wide_GoNo_MainPREPOSTexampleT %>% select(HotRTmean,PRE.POST1)

Wide_GoNo_MainPREPOSTexample <- Wide_GoNo_MainPREPOSTexample %>% 
  spread(PRE.POST1,HotRTmean)

```
